---
title: Monthly Attendance Summary

output:
  html_document:
      css: "../styles/styles.css"
params:
  date: !r Sys.Date()
---

```{r setup,echo=FALSE,message=FALSE,warning=FALSE}
source("setup.R")
```
For the previous month, tabulate attendance for each Member, broken down by weekday, social, and holiday.  Holiday hours are any hours on a holiday -- a list of holiday dates is maintained by the GOC.  Social hours are hours on weekends that are not holidays.  Workday hours are hours on non-weekends that are not holidays.
```{r dates}

start_date <- floor_date(params$date, 'month')
end_date <- ceiling_date(params$date, 'month') - days(1)
```
# Monthly Attendance Summary for `r format(start_date,"%B, %Y")`
```{r summary}

contacts <- get.contacts() %>%
  filter(grepl("Member", c2_groups))

summary <- get.attendance(days=65) %>%
  filter(as_date(da_date_of_attendance) %within% (start_date %--% end_date)) %>%
  filter(da_total_hours < 24) %>%
  inner_join(contacts, by = c("contact_2_id" = "id")) %>%
  mutate(RowWorkDayHrs = ifelse(!(da_date_of_attendance %in% holidays) &
    (wday(da_date_of_attendance) > 1 &
      wday(da_date_of_attendance) < 7), da_total_hours, 0)) %>%
  mutate(RowSocialHrs = ifelse(!(da_date_of_attendance %in% holidays) &
    (wday(da_date_of_attendance) == 1 |
      wday(da_date_of_attendance) == 7), da_total_hours, 0)) %>%
  mutate(RowHolidayHrs = ifelse(da_date_of_attendance %in% holidays, da_total_hours, 0)) %>%
  group_by(contact2_full_name) %>%
  summarise(
    WorkDayHrs = sum(RowWorkDayHrs), SocialHrs = sum(RowSocialHrs), HolidayHrs = sum(RowHolidayHrs),
    TotalHrs = sum(da_total_hours)
  ) %>%
  bind_rows(summarise(., across(where(is.numeric), sum), across(where(is.character), ~"Total")))

summary[which(summary[, "contact2_full_name"] == "Total"), 1] <-
  paste("Totals for", nrow(summary[, "contact2_full_name"]) - 1, "Members")

ft <- goc.table(summary, paste0("Monthly Attendance Summary for ", format(start_date, "%B, %Y")))
ft
```
