---
title: Supported Employment Billing `r format(params$date,"%B, %Y")`
output:
  html_document:
      css: "../styles/styles.css"
params:
  date: !r Sys.Date()
---

```{r setup,echo=FALSE,message=FALSE,warning=FALSE}
source("setup.R")
```
Data required by LSF for monthly supplemental employment billing.  Data comes from:

1. Members -- **member names, ids, benefits**
1. Attendance -- only **members that attend in the current month** are included
1. Supports -- **pre-employment and employment supports** are summarized
1. Employment -- **employment records** are displayed
1. Goals -- **employment goal updates** are summarized
1. Contacts -- **employer name**

To Do (Data)

1. Clean the member employment goals -- add goals if needed, check end dates, update goals
1. Add benefit data to member records
1. Add employment assessment info on employment records
1. Add employment supports as needed

To do (Clubhouse)

1. Establish documented processes for collecting, checking, and reporting all data needed by the supplemental employment report

```{r get-data}
start_date <- floor_date(params$date, "month")
end_date <- ceiling_date(params$date, "month") - days(1)

ndays <- as.integer(as_date(Sys.Date())-as_date(start_date)) +1

members <- get.members() %>%
  mutate(Benefits = ifelse(flo_ssi == "yes" | flo_ssdi == "yes" |
    flo_food_stamps == "yes" | flo_housing_voucher == "yes", "Yes", "No")) %>%
  select(id, contact_flourish_number, contact_id_c, last_name, first_name, Benefits)

# ft <- goc.table(members)
# ft

  attendance <- get.attendance(days=ndays) %>%
    filter(as_date(da_date_of_attendance) %within% (start_date %--% end_date)) %>%
    mutate(da_date_of_attendance = as_date(da_date_of_attendance)) %>%
    select(contact_2_id, da_date_of_attendance)

members <- members %>%
  inner_join(attendance, by = c("contact_id_c" = "contact_2_id")) %>%
  group_by(id, contact_flourish_number, contact_id_c, last_name, first_name, Benefits) %>%
  summarise(LastVisit = max(da_date_of_attendance)) %>%
  ungroup() %>%
  arrange(last_name, first_name)

# ft <- goc.table(members, paste0(nrow(members), " Attending Members"))
# ft

supports <- get.supports() %>%
  filter(as_date(flo_support_date) %within% (start_date %--% end_date)) %>%
  filter(flo_support_type == "Employment_readiness" |
    flo_support_type == "Employment_TE" |
    flo_support_type == "Employment_IE" |
    flo_support_type == "Employment_SE") %>%
  mutate(Pre = ifelse(flo_support_type == "Employment_readiness", "Yes", "No")) %>%
  mutate(SES = ifelse(flo_support_type != "Employment_readiness", "Yes", "No")) %>%
  select(id, sa_contacts_2_id, Pre, SES, flo_support_date)

support.rel <- get.table("flo_supports_contacts_c") %>%
  select("flo_supports_contactsflo_supports_ida", "flo_supports_contactscontacts_idb")

# support id is flo_supports_contactsflo_supports_ida
# member id is flo_supports_contactscontacts_idb


members <- members %>%
  left_join(support.rel, by = c("id" = "flo_supports_contactscontacts_idb")) %>%
  left_join(supports, by = c("flo_supports_contactsflo_supports_ida" = "id")) %>%
  select(-flo_supports_contactsflo_supports_ida) %>%
  group_by(id, contact_flourish_number, contact_id_c, last_name, first_name, LastVisit, Benefits) %>%
  summarise(Pre = max(Pre, na.rm = T), SES = max(SES, na.rm = T), MostRecentSupport = max(flo_support_date, na.rm=T)) %>%
  ungroup() %>%
  mutate(Pre = ifelse(Pre == -Inf | is.na(Pre), "No", Pre)) %>%
  mutate(SES = ifelse(SES == -Inf | is.na(SES), "No", SES))

goals <- get.goals()[,c("contact_id", "flo_goal_type", "flo_goal_end_date", "date_modified")] %>%
  filter(flo_goal_type == "Employment") %>%
  filter(!is.na(flo_goal_end_date) & as_date(flo_goal_end_date) <= end_date) %>%
  filter(!is.na(date_modified) & as_date(date_modified) <= end_date) 
  
members <- members %>%
  left_join(goals, by = c("id"="contact_id")) %>%
  group_by(id, contact_flourish_number, contact_id_c, last_name, first_name, LastVisit, Benefits, Pre, SES, MostRecentSupport) %>%
  summarise(DischargeDate = max(as_date(flo_goal_end_date), na.rm=T),
            EmploymentPlanUpdate = max(date_modified, na.rm=T)) %>%
  mutate(DischargeDate = as_date(ifelse(DischargeDate == -Inf, NA, DischargeDate)),
         EmploymentPlanUpdate = as_date(ifelse(EmploymentPlanUpdate == -Inf, NA, EmploymentPlanUpdate)))

# ft <- goc.table(members, paste0(nrow(members), " Add goal info ", format(params$date,"%B, %Y")))
# ft

assess <- get.employment()[,c("contact_id", "emp_assessment_date")] %>%
  group_by(contact_id) %>%
  summarise(RecentAssess = max(emp_assessment_date, na.rm=T)) %>%
  ungroup()

members <- members %>%
  left_join(assess, by=c("id" = "contact_id"))

# Employment records

members <- members %>%
  left_join(get.employment()[, c(
    "contact_id", "flo_emp_date_start",
    "flo_emp_job_title",
    "flo_emp_date_end", "flo_emp_job_title",
    "flo_emp_approximate_hourly_pay",
    "flo_emp_approximate_hours_wk",
    "employer_id"
  )], by = c("id" = "contact_id")) %>%
  left_join(get.contacts()[, c("id", "contact2_full_name")], by = c("employer_id" = "id"))

# ft <- goc.table(members, paste0(nrow(members), " Attending Members in ", format(params$date, "%B, %Y")))
# ft

# Finalize presentation

members <- members %>%
  arrange(last_name, first_name) %>%
  ungroup() %>%
  rename(`Client's Last Name` = last_name, 
         `Client's First Name` = first_name,
         `Client ID` = contact_flourish_number,
         `Most Recent Clubhouse Attendance Date` = LastVisit, 
         `Did this Client Receive Pre-Employment Supports this Month? (Yes/No)` = Pre, 
         `Is This Client Receiving Benefits?` = Benefits,
         `Did This Client Receive Supported Employment Services this Month? (Yes/No)` = SES,
         `Most Recent Supported Employment Service Date` = MostRecentSupport, 
         `Start Date of Most Recent Job` = flo_emp_date_start,
         `End Date of Most Recent Job` = flo_emp_date_end,
         `Supported Employment Initial Assessment Completion Date` = RecentAssess,
         `Employer Name` = contact2_full_name,
         `Supported Employment Initial Service Plan Creation Date` = EmploymentPlanUpdate,
         `Supported Employment Discharge Date` = DischargeDate,
         `Job Title` = flo_emp_job_title,
         `Average # Hours Worked Per Week` = flo_emp_approximate_hours_wk,
         `Hourly Pay` = flo_emp_approximate_hourly_pay,
         ) %>%
  select(`Client's Last Name`, 
         `Client's First Name`, 
         `Client ID`, 
         `Most Recent Clubhouse Attendance Date`, 
         `Did this Client Receive Pre-Employment Supports this Month? (Yes/No)`, 
         `Is This Client Receiving Benefits?`,
         `Did This Client Receive Supported Employment Services this Month? (Yes/No)`,
         `Supported Employment Initial Assessment Completion Date`,
         `Supported Employment Initial Service Plan Creation Date`,
         `Most Recent Supported Employment Service Date`,
         `Supported Employment Discharge Date`,
         `Start Date of Most Recent Job`,
         `End Date of Most Recent Job`,
         `Employer Name`,
         `Job Title`,
         `Average # Hours Worked Per Week`,
         `Hourly Pay`,
         -id,
         -contact_id_c
         )

ft <- goc.table(members, paste0(nrow(members), " Attending Members in ", format(params$date, "%B, %Y")))
ft
```
