---
title: "Load Members"
header-includes:
- \usepackage{pdflscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
output:
  html_document: default
  word_document: 
    reference_docx: word-styles.docx
    keep_md: yes
  pdf_document: default
---

```{r setup,echo=F,message=F,warning=F}
knitr::opts_chunk$set(echo=FALSE, message=FALSE,warning=FALSE,fig.width=14)
load("~/Documents/GOC/.RData")
library(knitr)
library(rmarkdown)
library(tidyverse)
library(kableExtra)
library(lubridate)
library(stringr)
library(RMySQL)
library(flextable)
library(uuid)
previous_month <- rollback(today()-months(1),roll_to_first =TRUE) %--% rollback(today())
holidays<-ymd(list("2022-01-17", "2022-05-30", "2022-06-20", "2022-07-04", "2022-09-05", 
                   "2023-01-16", "2023-05-29", "2023-06-16", 
                   "2023-07-04", "2023-09-04", "2023-10-09", "2023-11-10", "2023-11-23", "2023-11-24", "2023-12-25"))
 make_DT <- function(date,time_string) {
  # Given a date and a time string of the kind we see in contacts data, return a datetime
  d <- date
  hour(d)<-as.integer(substring(time_string,1,2))
  minute(d)<-as.integer(substring(time_string,4,5))
  d
 }
 set_flextable_defaults(
  font.size = 10, theme_fun = theme_zebra,
  padding = 6,
  background.color = "#EFEFEF")
```
# Extract, Transform and Load.  From Applistic to Flourish.  Intended for one-time use.

This is the first load script.  Member UUIDs are used in other loads to reference Members (goals&plans, support, progress notes). Members
are loaded before contacts, because Members must then be loaded into Contacts.  Flourish starts with Members.
```{r extract_members}
members <- read_csv("../data/applistic/people.csv", col_types = list(Race3="c",ProviderTitle="c",ProviderSuffix="c",
                                                             Referral="c",Race8="c",Race9="c",Race12="c",Race13="c",
                                                             Race14="c", StaffIDNumber="c")) %>%
  mutate(Member=Member=="Member") %>% mutate(Member = Member & !is.na(Member)) %>%
  mutate(Other= !Member & !Staff) %>%
  filter(PersonID != 1974) %>%
  rows_update(tibble(PersonID=2,Staff=F),by="PersonID") %>% # Jeff Lander was never an employee
  mutate(PersonType=ifelse(Member,"Member",ifelse(Staff,"Staff","Other"))) %>%
  mutate(DateRecCreated=mdy(DateRecCreated)) %>%
  mutate(Year=year(DateRecCreated)) %>%
  filter(PersonType=="Member")
members
```
# Tranform Members

There are many columns.  Not all are used by GOC.  Not all are populated in Applistic.  We will transform those of interest for loading to Flourish.
We will likely transform in batches or slices, adding more relevant variables as we go.

First interest is contact information.
```{r transform_members}
##   [1] "id"                             "date_entered"                  
##   [3] "date_modified"                  "modified_user_id"              
##   [5] "created_by"                     "description"                   
##   [7] "deleted"                        "assigned_user_id"              
##   [9] "salutation"                     "first_name"                    
##  [11] "last_name"                      "photo"                         
##  [13] "do_not_call"                    "phone_home"                    
##  [15] "phone_mobile"                   "phone_work"                    
##  [17] "phone_other"                    "primary_address_street"        
##  [19] "primary_address_city"           "primary_address_state"         
##  [21] "primary_address_postalcode"     "primary_address_country"       
##  [23] "reports_to_id"                  "birthdate"                     
##  [25] "campaign_id"                    "portal_account_disabled"       
##  [27] "portal_user_type"               "flo_transportation_mode_c"     
##  [29] "flo_housing_comments"           "flo_highest_grade_completed"   
##  [31] "flo_degrees_certificates"       "flo_education_comments"        
##  [33] "flo_ever_employed"              "flo_last_employment"           
##  [35] "flo_employment_comments"        "flo_annual_income"             
##  [37] "flo_food_stamps"                "flo_ssi"                       
##  [39] "flo_ssdi"                       "flo_housing_voucher"           
##  [41] "agency_id_c"                    "flo_agency_comments"           
##  [43] "flo_diagnosis_comments"         "flo_accessibility_restrictions"
##  [45] "referral_source_id_c"           "refererr_id_c"                 
##  [47] "flo_resume_link"                "flo_application_link"          
##  [49] "flo_release_link"               "flo_emergency_release"         
##  [51] "flo_information_release"        "flo_media_release"             
##  [53] "flo_application_date"           "member_address_street"         
##  [55] "member_address_street_2"        "member_address_street_3"       
##  [57] "member_address_city"            "member_address_state"          
##  [59] "member_address_postalcode"      "member_address_country"        
##  [61] "emergency_address_street"       "emergency_address_city"        
##  [63] "emergency_address_state"        "emergency_address_postalcode"  
##  [65] "emergency_address_country"      "flo_nickname_preferred_name_c" 
##  [67] "flo_middle_name_c"              "flo_preferred_pronouns_c"      
##  [69] "flo_preferred_language_c"       "flo_unit_chosen_by_member_c"   
##  [71] "flo_membership_status_c"        "flo_approved_contact_methods_c"
##  [73] "flo_preferred_phone_c"          "flo_phone_number_4_c"          
##  [75] "flo_phone_number_5_c"           "flo_race_c"                    
##  [77] "flo_ethnicity_hispanic_c"       "flo_gender_identity_c"         
##  [79] "flo_gender_at_birth_c"          "flo_type_young_adults_c"       
##  [81] "flo_type_senior_citizen_c"      "flo_considered_veteran_c"      
##  [83] "flo_considered_lgbt_c"          "flo_marital_status_c"          
##  [85] "flo_housing_status_c"           "flo_highest_level_of_educati_c"
##  [87] "flo_billing_code_c"             "flo_deceased_c"                
##  [89] "flo_external_id1_c"             "flo_external_id2_c"            
##  [91] "flo_emergency_contact_c"        "flo_emergency_con_phone_c"     
##  [93] "contact_id_c"                   "contact_autoincrement"         
##  [95] "contact_flourish_number"        "flo_contact_record_type_c"     
##  [97] "avg_time_at_ch"                 "flo_race_mult"                 
##  [99] "flo_preferred_pronouns_dd"      "flo_primary_language_c"        
## [101] "flo_secondary_language_c"       "flo_preferred_contact_methods" 
## [103] "flo_diagnoses_mult"             "flo_allergies"                 
## [105] "flo_primary_phone"              "flo_secondary_phone"           
## [107] "flo_email_opt_out_c"            "flo_mail_opt_out_c"            
## [109] "birthday_month"                 "age"

#
#  To add variables, likely will pull members from Flourish, tack on columns from Applistic and push the whole thing back in.
#

# transformed.members <- members %>%
#     mutate(id = UUIDgenerator(n=n()) %>%
#     mutate(date_entered = now()) %>%
#     mutate(date_modified = now()) %>%
#     mutate(name = paste0("Member-",seq(1,n()))) %>%
#     select(id,name,date_entered,date_modified)
# ft <- flextable(head(transformed.members)) %>% autofit()
# ft
```

# Connect to Flourish and write the members data to Flourish.

Members are written to "contacts" in Flourish.  Flourish was a born as a CRM and contacts is the central file.

(Our "contacts" -- mostly donors, vendors, prospects are in a separate file.  Members are also contacts)
```{r load_members}

# # Make a database connection to Flourish
# con <- dbConnect(RMySQL::MySQL(),
#                        dbname = "gainesville_db",
#                        host = "3.136.184.221",
#                        port = 3306,
#                        user = "mikeconlon",
#                        password = "c8g8*uKkm4s4NM")
# 
# # Allow Tables to be loaded from R
# dbSendQuery(con, "SET GLOBAL local_infile = true;")
# 
# # Load members to Flourish replacing whatever is there. value is R, name is remote table
# dbWriteTable(con, value = transformed.members, name = 'contacts_test', append = T, row.names = F)
# 
# # Drop the test table
# # dbSendQuery(con, "DROP TABLE contacts_test")
# 
# dbDisconnect(con)
```