---
title: "Load Contacts from Applistic and AirTable"
header-includes:
- \usepackage{pdflscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
output:
  html_document: default
  word_document: 
    reference_docx: word-styles.docx
    keep_md: yes
  pdf_document: default
---

```{r setup,echo=F,message=F,warning=F}
knitr::opts_chunk$set(echo=FALSE, message=FALSE,warning=FALSE,fig.width=14)
load("~/Documents/GOC/.RData")
library(knitr)
library(rmarkdown)
library(tidyverse)
library(kableExtra)
library(lubridate)
library(stringr)
library(RMySQL)
library(flextable)
library(uuid)
previous_month <- rollback(today()-months(1),roll_to_first =TRUE) %--% rollback(today())
holidays<-ymd(list("2022-01-17", "2022-05-30", "2022-06-20", "2022-07-04", "2022-09-05", 
                   "2023-01-16", "2023-05-29", "2023-06-16", 
                   "2023-07-04", "2023-09-04", "2023-10-09", "2023-11-10", "2023-11-23", "2023-11-24", "2023-12-25"))
 make_DT <- function(date,time_string) {
  # Given a date and a time string of the kind we see in contacts data, return a datetime
  d <- date
  hour(d)<-as.integer(substring(time_string,1,2))
  minute(d)<-as.integer(substring(time_string,4,5))
  d
 }
 set_flextable_defaults(
  font.size = 10, theme_fun = theme_zebra,
  padding = 6,
  background.color = "#EFEFEF")
```
# Extract, Transform and Load.  From Applistic to Flourish.  Intended for one-time use.

1. Extract contacts from Applistic.  Format for Flourish 
2. Extract contacts from AirTable. Format for Flourish
3. Combine the two datasets.  For Member data favor Applistic.  For others favor AirTable.
4. Prepare the combined dataset for Flourish
5. Map to Fourish variables
6. Load to a test dataset

```{r extract_applistic_contacts}
applistic.contacts <- read_csv("../data/applistic-final/people.csv", col_types = list(Race3="c",ProviderTitle="c",ProviderSuffix="c",
                                                             Referral="c",Race8="c",Race9="c",Race12="c",Race13="c",
                                                             Race14="c", StaffIDNumber="c")) %>%
  mutate(Member=Member=="Member") %>% mutate(Member = Member & !is.na(Member)) %>%
  mutate(Other= !Member & !Staff) %>%
  mutate(FullName=paste(ifelse(is.na(PersonTitle),"",PersonTitle),
                    ifelse(is.na(FirstName),"",FirstName),
                    ifelse(is.na(MiddleName),"",MiddleName),
                    ifelse(is.na(LastName),"",LastName),
                    ifelse(is.na(NameSuffix),"",NameSuffix))) %>%
  filter(PersonID != 1974) %>%
  rows_update(tibble(PersonID=2,Staff=F),by="PersonID") %>% # Jeff Lander was never an employee
  rename(Nickname=NickName) %>%
  mutate(PersonType=ifelse(Member,"Member",ifelse(Staff,"Staff","Other"))) %>%
  mutate(Notes=ContactNotes) %>%
  mutate(Country="US",Salutation="") %>%
  mutate(DateRecCreated=mdy(DateRecCreated)) %>%
  mutate(Groups="") %>%
  mutate(Solicit=TRUE) %>%
  mutate(ContactType="Person") %>%
  mutate(Groups= ifelse(Board, paste0("^GOC Board Member^,",Groups), Groups)) %>%
  mutate(Groups= ifelse(CaseMngr, paste0("^Case Manager^,",Groups), Groups)) %>%
  mutate(Groups= ifelse(Member, paste0("^GOC Member^,",Groups), Groups)) %>%
  mutate(Groups= ifelse(Staff, paste0("^GOC Staff^,",Groups), Groups)) %>%
  mutate(Groups= ifelse(Volunteer, paste0("^GOC Volunteer^,",Groups), Groups)) %>%
  select(PersonID,ContactType,FullName,Salutation,FirstName,LastName,Nickname,Groups,StreetAddress,City,State,ZipCode,Country,PhoneNumber,CellPhone,
         WorkPhone,Email,Email2,Solicit,Notes) %>%
  arrange(LastName,FirstName)
applistic.contacts
ft<-flextable(head(applistic.contacts)) %>% autofit()
ft
```

```{r extract_airtable_contacts}
airtable.contacts <- read_csv("../data/airtable/Contacts-All Contacts.csv") %>%
    mutate(PersonID=seq(from=3000,length.out=n())) %>%
    mutate(Solicit=(ifelse(Solicit=="checked",T,F))) %>%
    rename(FirstName=`First Name`,LastName=`Last Name`,PhoneNumber=Phone,ContactType=`Contact Type`,FullName=Name) %>%
    mutate(CellPhone="", WorkPhone="", Email2="", Nickname="") %>%
    rename(GroupsString=Groups) %>%
    mutate(GroupsString=ifelse(grepl(",Member,",GroupsString),paste0("GOC Member,",GroupsString),GroupsString)) %>%
    mutate(GroupsString=ifelse(GroupsString=="Member","GOC Member",GroupsString)) %>%
    mutate(GroupsString=ifelse(startsWith(GroupsString,"Member,"),paste0("GOC Member,",GroupsString),GroupsString)) %>%
    mutate(Groups="") %>%
    mutate(Groups= ifelse(grepl("FCC",GroupsString), paste0("^FCC^,",Groups), Groups)) %>%
    mutate(Groups= ifelse(grepl("GOC Member",GroupsString), paste0("^GOC Member^,",Groups), Groups)) %>%
    mutate(Groups= ifelse(grepl("Donor",GroupsString), "^Donor^", Groups)) %>%
    mutate(Groups= ifelse(grepl("Rotary",GroupsString), paste0("^Rotary^,",Groups), Groups)) %>%
    mutate(Groups= ifelse(grepl("GOC Board Member",GroupsString), paste0("^GOC Board Member^,",Groups), Groups)) %>%
    mutate(Groups= ifelse(grepl("GOC Staff",GroupsString), paste0("^GOC Staff^,",Groups), Groups)) %>%
    mutate(Groups= ifelse(grepl("GOC Volunteer",GroupsString), paste0("^GOC Volunteer^,",Groups), Groups)) %>%
    mutate(Groups= ifelse(grepl("Mental Health",GroupsString), paste0("^Mental Health^,",Groups), Groups)) %>%
    mutate(Groups= ifelse(grepl("Vendor",GroupsString), paste0("^Vendor^,",Groups), Groups)) %>%
    mutate(Groups= ifelse(grepl("Deceased",GroupsString), paste0("^Deceased^,",Groups), Groups)) %>%
    mutate(Groups= ifelse(grepl("Former Board Member",GroupsString), paste0("^Former GOC Board Member^,",Groups), Groups)) %>%
    mutate(Groups= ifelse(grepl("Former Staff",GroupsString), paste0("^Former GOC Staff^,",Groups), Groups)) %>%
    mutate(Groups= ifelse(grepl("Newsletter",GroupsString), paste0("^Newsletter^,",Groups), Groups)) %>%
    select(PersonID,ContactType,FullName,Salutation,FirstName,LastName,Nickname,Groups,StreetAddress,City,State,ZipCode,Country,PhoneNumber,CellPhone,
           WorkPhone,Email,Email2,Solicit,Notes) %>%
    arrange(LastName, FirstName)
airtable.contacts
# ft<-flextable(head(airtable.contacts)) %>% autofit()
# ft
```

```{r combine_contacts}
applistic.contacts.members <- applistic.contacts %>% filter(grepl("GOC Member",Groups))
applistic.contacts.members
airtable.contacts.not_members <- airtable.contacts %>% filter(!grepl("GOC Member",Groups)==T)
airtable.contacts.not_members
applistic.contacts.other <- applistic.contacts %>% filter(!grepl("GOC Member",Groups)==T) %>% anti_join(airtable.contacts.not_members,by=c("FirstName","LastName")) %>% arrange(PersonID)
applistic.contacts.other
contacts <- applistic.contacts.members %>% bind_rows(airtable.contacts.not_members) %>% bind_rows(applistic.contacts.other) %>% arrange(PersonID)
contacts
write_csv(contacts,file="../output/untransformed-contacts.csv")
```

```{r transform_contacts}
##  [1] "id"                         "date_entered"              
##  [3] "date_modified"              "modified_user_id"          
##  [5] "created_by"                 "description"               
##  [7] "deleted"                    "assigned_user_id"          
##  [9] "salutation"                 "first_name"                
## [11] "last_name"                  "photo"                     
## [13] "do_not_call"                "phone_home"                
## [15] "phone_mobile"               "phone_work"                
## [17] "phone_other"                "primary_address_street"    
## [19] "primary_address_city"       "primary_address_state"     
## [21] "primary_address_postalcode" "primary_address_country"   
## [23] "c2_groups"                  "c2_address_street"         
## [25] "c2_address_street_3"        "c2_address_city"           
## [27] "c2_address_state"           "c2_address_postalcode"     
## [29] "c2_address_country"         "c2_primary_phone"          
## [31] "c2_secondary_phone"         "c2_address_street_2"       
## [33] "c2_contact_record_type_c"   "c2_salutation"
transformed.contacts <- contacts %>%
    mutate(id = UUIDgenerate(n=n())) %>%
    mutate(date_entered = now()) %>%
    mutate(date_modified = now()) %>%
    mutate(modified_user_id = "") %>%
    mutate(created_by = "") %>%
    mutate(description = "") %>%
    mutate(deleted = FALSE) %>%
    mutate(assigned_user_id = "") %>%
  
    mutate(salutation = "") %>%
    mutate(first_name = FirstName) %>%
    mutate(last_name = LastName) %>%
    mutate(photo = "") %>%
    mutate(do_not_call=F) %>%
    mutate(phone_home = PhoneNumber) %>%
    mutate(phone_mobile = CellPhone) %>%
    mutate(phone_work = "") %>%
    mutate(phone_other = "") %>%
    
    mutate(primary_address_street=StreetAddress) %>%
    mutate(primary_address_city=City) %>%
    mutate(primary_address_state=State) %>%
    mutate(primary_address_postalcode=ZipCode) %>%
    mutate(primary_address_country=Country) %>%
    
    mutate(c2_groups=Groups) %>%
    mutate(c2_address_street=StreetAddress) %>%
    mutate(c2_address_street_3="") %>%
    mutate(c2_address_city=City) %>%
    mutate(c2_address_state=State) %>%
    mutate(c2_address_postalcode=ZipCode) %>%
    mutate(c2_address_country=Country) %>%
    mutate(c2_primary_phone=PhoneNumber) %>%
    mutate(c2_secondary_phone=CellPhone) %>%
    mutate(c2_address_street_2="") %>%
    mutate(c2_contact_record_type_c=ContactType) %>%
    mutate(c2_salutation=Salutation) %>%
  
    mutate(c2_person_id=PersonID) %>%
    mutate(c2_full_name=FullName) %>%
    mutate(c2_nickname=Nickname) %>%
  
    select(id,date_entered,date_modified,modified_user_id,created_by,description,deleted,assigned_user_id,salutation,
           first_name,last_name,photo,do_not_call,phone_home,phone_mobile,phone_work,phone_other,primary_address_street,
           primary_address_city,primary_address_state,primary_address_postalcode,primary_address_country,c2_groups,
           c2_address_street,c2_address_street_3,c2_address_city,c2_address_state,c2_address_postalcode,c2_address_country,
           c2_primary_phone,c2_secondary_phone ,c2_address_street_2,c2_contact_record_type_c,c2_salutation,c2_person_id,
           c2_full_name,c2_nickname)

ft <- flextable(head(transformed.contacts)) %>% autofit()
ft
write_csv(transformed.contacts,file="../output/transformed-contacts.csv")
```

# Connect to Flourish and write the contacts data to Flourish
```{r load_contacts}

# # Make a database connection to Flourish
# con <- dbConnect(RMySQL::MySQL(),
#                        dbname = "gainesvillecrm",
#                        host = "3.136.184.221",
#                        port = 3306,
#                        user = "mikeconlon",
#                        password = "c8g8*uKkm4s4NM")
# 
# # Allow Tables to be loaded from R
# dbSendQuery(con, "SET GLOBAL local_infile = true;")
# 
# # Load contacts to Flourish replacing whatever is there. value is R, name is remote table
# dbWriteTable(con, value = transformed.contacts, name = 'contacts_test', append = T, row.names = F)
# 
# 
# dbDisconnect(con)
```