---
title: "Load Goals and Plans"
header-includes:
- \usepackage{pdflscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
output:
  html_document: default
  word_document: 
    reference_docx: word-styles.docx
    keep_md: yes
  pdf_document: default
---

```{r setup,echo=F,message=F,warning=F}
knitr::opts_chunk$set(echo=FALSE, message=FALSE,warning=FALSE,fig.width=14)
load("~/Documents/GOC/.RData")
library(knitr)
library(rmarkdown)
library(tidyverse)
library(kableExtra)
library(lubridate)
library(stringr)
library(RMySQL)
library(flextable)
library(uuid)
set_flextable_defaults(font.size = 10, theme_fun = theme_zebra, padding = 6, background.color = "#EFEFEF")
```
# Extract, Transform and Load. From Applistic to Flourish. Intended for one-time use.

Goals are loaded after contacts to be able to associate goals with their Member and Staff Member.

The Applistic action plan goal is like the Flourish goal. The Applistic action plan is a "header" that contains the member and staff member references.
```{r extract_goals}

action_plan_goals <- read_csv("../data/applistic-final/action_plan_goals.csv") %>%
    rename(ActionPlanID=RelatedActionPlanID) %>%
    mutate(CompletionDueDate=ifelse(startsWith(CompletionDueDate,"####"),NA,CompletionDueDate)) %>%
    mutate(`Record Creation Date`=ifelse(startsWith(`Record Creation Date`,"####"),NA,`Record Creation Date`)) %>%
    mutate(StartDate=mdy(StartDate)) %>%
    
    # Recode Goal Status
    
    mutate(GoalStatus=ifelse(is.na(GoalStatus),"Unknown",GoalStatus)) %>%
    mutate(GoalStatus=ifelse(GoalStatus == "Goal Active","In_progress",
                             ifelse(GoalStatus == "Goal Not Reached","Not_completed",
                                    ifelse(GoalStatus == "Goal Reached","Finished","Unknown")))) %>%
    
    # Recode GoalType
    
    mutate(GoalType=ifelse(is.na(GoalType),"Unknown",GoalType)) %>%
    mutate(GoalType=ifelse(GoalType == "Educational","Education", GoalType)) %>%
    mutate(GoalType=ifelse(GoalType == "Employment / Education","Education", GoalType)) %>%
    mutate(GoalType=ifelse(GoalType == "Financial","Financial", GoalType)) %>%
    mutate(GoalType=ifelse(GoalType == "Health / Mental","Health_mental", GoalType)) %>%
    mutate(GoalType=ifelse(GoalType == "Health / Physical","Health_physical", GoalType)) %>%
    mutate(GoalType=ifelse(GoalType == "Living Situation","Housing", GoalType)) %>%
    mutate(GoalType=ifelse(GoalType == "Personal Employment Plan","Employment", GoalType)) %>%
    mutate(GoalType=ifelse(GoalType == "Social","Social", GoalType)) %>%
    mutate(GoalType=ifelse(GoalType == "Spiritual / Recreational","Spiritual", GoalType)) %>%
    
    mutate(CompletionDueDate=mdy(CompletionDueDate)) %>%
    mutate(CompletionDate=mdy(CompletionDate)) %>%
    mutate(`Last Update`=mdy(`Last Update`)) %>%
    mutate(`Record Creation Date`=mdy(`Record Creation Date`))

action_plan_goals
# ft <- goc.table(action_plan_goals,"Goals")
# ft

action_plans <- read_csv("../data/applistic-final/action_plans.csv") %>%
     mutate(TargetCompletionDate=mdy(TargetCompletionDate)) %>%
     mutate(ClosureDate=mdy(ClosureDate)) %>%
     mutate(LastReview=mdy(LastReview)) %>%
     mutate(LastUpdate=mdy(LastUpdate)) %>%
     mutate(DateRecCreated=mdy(DateRecCreated))

action_plans
# ft <- goc.table(action_plans,"Plans")
# ft

goals <- action_plan_goals %>% 
    left_join(action_plans, by="ActionPlanID") %>%
    rename(GoalStatus=GoalStatus.x) %>%
    mutate(MemberID=as.character(MemberID)) %>%
    mutate(AdvisorID=as.character(AdvisorID))

# goals
# 
# 
# tab <- goals %>%
#     group_by(GoalStatus) %>%
#     tally()
# tab <- goc.table(tab,"Goal Status")
# tab
# 
# tab <- goals %>%
#     group_by(GoalType) %>%
#     tally()
# tab <- goc.table(tab,"Goal Type")
# tab

# ft <- goc.table(goals,"Goals and Plans before joins")
# ft

```

# Add a chunk here to join on the legacy MemberID to match the member
```{r join-member-ids}
# Get the members from Flourish
con <- dbConnect(RMySQL::MySQL(),
                       dbname = "gainesvillecrm",
                       host = "3.136.184.221",
                       port = 3306,
                       user = "mikeconlon",
                       password = "c8g8*uKkm4s4NM")

members <- dbGetQuery(con, "SELECT * FROM contacts") %>%
    rename(contact_id=id) %>%
    select(contact_id,flo_external_id1_c)

dbDisconnect(con)


goals <- goals %>%
    left_join(members,by=c("MemberID"="flo_external_id1_c"))

# goals
# ft <-goc.table(goals)
# ft

```

# Add a chunk here to join on the contact_2_ids ids to match the staff member
```{r join-contact-ids}
# Get the contacts from Flourish
con <- dbConnect(RMySQL::MySQL(),
                       dbname = "gainesvillecrm",
                       host = "3.136.184.221",
                       port = 3306,
                       user = "mikeconlon",
                       password = "c8g8*uKkm4s4NM")

contacts <- dbGetQuery(con, "SELECT * FROM sa_contacts_2") %>%
    rename(contact_2_id=id) %>%
    select(first_name,last_name,contact_2_id,contact2_applistic_number)

dbDisconnect(con)

# Renumber goes here

staff <-data.frame(StaffName=c("Brett","Maggie","Kyanna","Nakeshia","Cristina","Sandy","Brett","Maggie","Rose Ann","Robert",
                               "Kaitlyn","Mia","Kaitlyn","Paul","Deidra","Cristina","Kalya","Ouida","Roscoe","Jeff",
                               "Debbie","Brian","Jill","Fey","Chris","Luis","Kerry","Joseph","Robert","Barry"),
                  OldID=c("1469","1540","1633","1715","1729","1733","1822","1874","1964","1968",
                          "2026","2072","2074","2100","2076","1655","1997","1698","1425","664",
                          "1269","674","1326","1126","1154","1329","1408","312","625","649"),
                  NewID=c("3835","4038","1633","1715","3796","1733","3835","4038","1964","4039",
                          "4651","4553","4651","2100","4641","3796","3212","3907","3410","4336",
                          "4200","4025","3185","3998","4206","3603","3508","3837","3958","4130"))

contacts <- contacts %>%
    left_join(staff,by=c("contact2_applistic_number"="NewID")) %>%
    mutate(contact2_applistic_number = ifelse(!is.na(contact2_applistic_number),
                                              OldID,contact2_applistic_number)) %>%
    filter(!is.na(contact2_applistic_number))
    
contacts[,c("first_name","last_name","contact2_applistic_number")]

goals <- goals %>%
    left_join(contacts,by=c("AdvisorID"="contact2_applistic_number"))

ft <- goc.table(goals)
ft

```

# Tranform goals and plans

```{r transform_goals}

  
## [10] "contact_id"             "contact_2_id"           "flo_goal_creation_date"
## [13] "flo_goal_description"   "flo_goal_start_date"    "flo_goal_due_date"     
## [16] "flo_goal_type"          "flo_goal_status"        "flo_goal_action_plan"  
## [19] "flo_goal_needs"         "flo_goal_staff_support" "flo_goal_other_support"

transformed.goals <- goals %>%
    
    mutate(id = UUIDgenerate(n=n())) %>%
    mutate(name = paste0("Goal-",seq(1,n()))) %>%
    mutate(date_entered = Sys.time()) %>%
    mutate(date_modified = Sys.time()) %>%
    mutate(modified_user_id = "4cde6014-5735-b6a8-2975-63e1844134be") %>% # UUID for Mike Conlon
    mutate(created_by = "4cde6014-5735-b6a8-2975-63e1844134be") %>%
    mutate(description = "") %>%
    mutate(deleted = 0) %>%
    mutate(assigned_user_id = "") %>%

    rename(flo_goal_creation_date = `Record Creation Date`) %>%
    rename(flo_goal_description = Objective) %>%
    rename(flo_goal_due_date = TargetCompletionDate) %>%
    rename(flo_goal_start_date = StartDate) %>%
    rename(flo_goal_end_date = CompletionDate) %>%
    rename(flo_goal_type = GoalType) %>%
    rename(flo_goal_status = GoalStatus) %>%
    rename(flo_goal_action_plan = Action) %>%
    rename(flo_goal_needs = Resource) %>%
    rename(flo_goal_staff_support = ResponsiblePerson) %>%
    rename(flo_goal_other_support = OtherHelp) %>%
    
    select("id","name","date_entered","date_modified","modified_user_id","created_by","description","deleted",
           "assigned_user_id","contact_id","contact_2_id","flo_goal_creation_date","flo_goal_description",
           "flo_goal_start_date","flo_goal_due_date","flo_goal_type","flo_goal_status","flo_goal_action_plan",
           "flo_goal_needs","flo_goal_staff_support","flo_goal_other_support")

ft <- goc.table(transformed.goals,"Goals Ready to Load")
ft

tab <- transformed.goals %>%
    group_by(contact_2_id) %>%
    tally()
ft <- goc.table(tab)
ft


```


# Connect to Flourish and write the goals and plans data to Flourish

```{r load_goals}

# Make a database connection to Flourish
con <- dbConnect(RMySQL::MySQL(),
                       dbname = "gainesvillecrm",
                       host = "3.136.184.221",
                       port = 3306,
                       user = "mikeconlon",
                       password = "c8g8*uKkm4s4NM")

# Allow Tables to be loaded from R
dbSendQuery(con, "SET GLOBAL local_infile = true;")

# Load goals to Flourish replacing whatever is there. value is R, name is remote table

dbGetQuery(con,"DELETE FROM sa_goals;")
dbWriteTable(con, value = transformed.goals, name = 'sa_goals', append = T, row.names = F)

# Drop the test table


dbDisconnect(con)
```