---
title: Get Flourish Records
subtitle: For debugging and tabulating, cleaning and reporting
output:
  html_document:
    css: "../styles/styles.css"
---

```{r setup,echo=F,message=F,warning=F}
source("setup.R")
```
Each table we are using in Flourish has a corresponding "get" function, to get records from Flourish.  We use these functions to encapsulate database connections and disconnects, as well as to simplify access of only non-deleted records (the default) and to permit the getting of all records (use include.deleted=TRUE)

Each of the get functions uses two lower level functions -- flourish.connection, and get.table.  get.table calls flourish.connection and dbDisconnect. get.table can be used to get any table from Flourish.

RMySQL is a required library for these functions.

```{r flourish}
# flourish.connection <- function() {
#   dbConnect(RMySQL::MySQL(),
#     dbname = key_get("Flourish GOC production dbname"),
#     host = key_get("Flourish GOC production host"),
#     port = 3306,
#     user = key_get("Flourish GOC production user"),
#     password = key_get("Flourish GOC production password")
#   )
# }

get.table <- function(table.name, include.deleted = FALSE, where="") {
  # include.deleted -- TRUE, deleted records are included in the results, otherwise filtered

  con <- flourish.connection()

  suppressWarnings({

      table <- dbGetQuery(con, paste0("SELECT * FROM ", table.name, " ", where))
  
  })

  if (!include.deleted) {
    table <- table %>% filter(!deleted)
  }

  dbDisconnect(con)
  table
}

get.users <- function(include.deleted = FALSE) {
  get.table("users", include.deleted)
}

# users <-get.users()
# 
# ft <- goc.table(users)
# ft

get.members <- function(include.deleted = FALSE, active.only = FALSE) {
  members <- get.table("contacts", include.deleted)

  if (active.only) {
    recent.members <- members %>%
      filter(flo_deceased_c != "Yes") %>%
      filter(flo_membership_status_c != "On_leave") %>%
      inner_join(get.attendance(days=90), by = c("contact_id_c" = "contact_2_id")) %>% # Inner join must be a Member with attendance
      mutate(Since = Sys.Date() - as_date(da_date_of_attendance)) %>%
      rename(id = id.x) %>%
      group_by(id) %>%
      summarise(MostRecent = min(Since)) %>%
      select(id)
    members <- members %>%
      inner_join(recent.members, by = c("id" = "id"))
  }
  members
}

# tab <- get.members() %>%
#     group_by(flo_membership_status_c) %>%
#     tally()
# 
# ft <- goc.table(tab)
# ft
# 
# members <- get.members(active.only=T) %>%
#   select(first_name, last_name, flo_membership_status_c)
# 
# nrow(members)
# 
# ft <- goc.table(members,"Members")
# ft

get.attendance <- function(include.deleted = FALSE, days=Inf) {
  if (days == Inf) {
    get.table("sa_flourish_daily_attendance", include.deleted)
  } else {
    where <- paste0(" WHERE da_date_of_attendance >= DATE_SUB(NOW(), INTERVAL ",days," DAY);")
    get.table("sa_flourish_daily_attendance", include.deleted, where=where)
  }
}

# attendance <- get.attendance()
# 
# ft <- goc.table(tail(attendance), "Attendance")
# ft

get.outreach <- function(include.deleted = FALSE) {
  get.table("sa_flourish_reach_out", include.deleted)
}

# outreach <- get.outreach()
#
# ft <- goc.table(tail(outreach), "Outreach")
# ft

get.goals <- function(include.deleted = FALSE) {
  get.table("sa_goals", include.deleted)
}

# goals <- get.goals() %>%
#   group_by(flo_goal_type) %>%
#   tally()
# 
# ft <- goc.table(goals)
# ft


# goals <- get.goals()
#
# ft <- goc.table(goals, "Goals")
# ft

get.supports <- function(include.deleted = FALSE, with.members=FALSE) {
  
  supports <- get.table("flo_supports", include.deleted)
  
  if (with.members) {
    
    rel <- get.table("flo_supports_contacts_c")
    
    members <- get.members(include.deleted)
    
    supports <- supports %>%
      inner_join(rel, by = c("id"="flo_supports_contactsflo_supports_ida")) %>%
      inner_join(members, by=c("flo_supports_contactscontacts_idb"="id"))
  }
  
  supports
}

# supports <- get.supports(with.members=T) %>%
#   arrange(desc(flo_support_date))
# 
# nrow(supports)
# ft <- goc.table(head(supports,n=100), "Supports")
# ft

get.progress.notes <- function(include.deleted = FALSE) {
  get.table("flo_progress_notes", include.deleted)
}

# progress.notes <- get.progress.notes()
#
# ft <- goc.table(progress.notes, "Progress Notes")
# ft

get.contacts <- function(include.deleted = FALSE, include.email = T) {
  
  contacts <- get.table("sa_contacts_2", include.deleted)
  
  if (include.email) {
    email.addr.bean.rel <- get.table("email_addr_bean_rel") %>% filter(primary_address == 1)

    if (!include.deleted) {
      email.addr.bean.rel <- email.addr.bean.rel %>% filter(!deleted)
    }

    email.addr.bean.rel %>% select(bean_id, email_address_id)

    email.addresses <- get.table("email_addresses")

    if (!include.deleted) {
      email.addresses <- email.addresses %>% filter(!deleted)
    }

    email.addresses <- email.addresses %>% select(id, email_address)

    contacts <- contacts %>%
      left_join(email.addr.bean.rel, by = c("id" = "bean_id")) %>%
      left_join(email.addresses, by = c("email_address_id" = "id")) %>%
      rename(date_modified = date_modified.x, deleted = deleted.x) %>%
      select(
        -id.y, -email_address_id, -bean_module, -primary_address,
        -reply_to_address, -date_modified.y, -deleted.y, -date_created
      )
  }
  
  contacts
}

# contacts <- get.contacts(include.email=F)
# nrow(contacts)
# 
# ft <- goc.table(contacts,"Contacts")
# ft

get.gifts <- function(include.deleted = FALSE) {
  get.table("flo_gifts", include.deleted)
}

# gifts <- get.gifts()
#
# ft <- goc.table(gifts,"Gifts")
# ft

get.employment <- function(include.deleted = FALSE) {
  get.table("sa_employment", include.deleted)
}

# employment <- get.employment()
#
# ft <- goc.table(employment,"Gifts")
# ft
```
